---
title: "Whisky Data Analyics"
author: "Koki Ando"
date: "3/11/2018"
output:
  html_document:
    code_folding: show
    highlight: tango
    theme: cosmo
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hello, everybody. My name is Koki Ando. This is my first published. RMarkdown report.

I just wanted to analyze data about whisky, just because i love them.
So i searched a little bit on safari and found this site.
[Classification of whiskies](http://outreach.mathstat.strath.ac.uk/outreach/nessie/nessie_whisky.html)

Looks interesting, so let's get started!

## Preparation

```{r}
library(data.table)
library(tidyverse)
library(sp)
whisky <- fread("http://outreach.mathstat.strath.ac.uk/outreach/nessie/datasets/whiskies.txt", data.table = FALSE)
```

### What's inside the dataset

```{r}
whisky$Longitude <- as.numeric(whisky$Longitude)
whisky$Latitude <- as.numeric(whisky$Latitude)
str(whisky)
```

Looks like someone has reviewed 86 whisky and recorded. it will be so subjective and biased dataset for sure but, i dont care.
In terms of "data science", it is problematic. However, drinking and reviewing whisky is always subjective, and there is nothing wrong with it, right? I dont care. im doing this analytics because for having fun.

## Data Analysis
First of all, i want to see where the distilleries are located.

```{r}
library(maps)
world.map <- map_data ("world")
glimpse(world.map)
```

### Map Vizualization

```{r}
UK.map <- world.map %>% filter(region == "UK")

whiskies.coord <- data.frame(whisky$Latitude, whisky$Longitude)
coordinates(whiskies.coord) <- ~whisky.Latitude + whisky.Longitude

proj4string(whiskies.coord) <- CRS("+init=epsg:27700")
whiskies.coord <- spTransform(whiskies.coord, CRS("+init=epsg:4326"))

whisky.map <- 
  data.frame(Distillery = whisky$Distillery,
             lat = whiskies.coord$whisky.Latitude,
             long = whiskies.coord$whisky.Longitude)

UK.map %>%
  filter(subregion == "Scotland") %>% 
  ggplot() + 
  geom_map(map = UK.map, 
           aes(x = long, y = lat, map_id = region),
           fill="white", colour = "black") + 
  coord_map() + 
  geom_point(data = whisky.map, 
             aes(x=lat, y = long, colour = "red", alpha = .9))
```

[This report](http://www.statworx.de/whitepaper/reporting-mit-r-a-whisky-guide.html) helped me a lot.

ive never tasted over half of them, but i know some. Lets get into it.



### Making whisky dataset tidy

```{r}
whisky <- whisky %>% select(Distillery:Floral)
head(whisky)
```

```{r}
whisky.score <- whisky %>% 
  gather(key = Review.point, value = Score, Body:Floral)
head(whisky.score)
```

### Data Vizualization 

```{r fig.width=15, fig.height=15}
whisky.score %>% 
  ggplot(aes(x=Review.point, y = Score, fill = Review.point)) + 
  geom_bar(stat = "identity") + 
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + 
  facet_wrap(~ Distillery)
```


## Conclusion
I really enjoyed this analytics. it is so fun analyzing data about something im interested in.
Ive teaching myself R for months and a little bit surprised that im still loving it, to be honest. 
From now on, i want to share my R contents and hoppefully get connected with R lovers!

i will update this article in near future because i really want to do deeper analysis.

Here is my
[GitHub](https://github.com/koki25ando)
[kaggle](https://www.kaggle.com/koki25ando)

Thanks for reading my artice!

Koki





